### 2017-05-31 doc/response.tex

Weaknesses:
: 
The results of the paper are unfortunately fairly obvious. From the
omission score analysis, we learn that a model trained to predict the
next word in a sentence is sensitive to function words, while a word
trained to associate a sentence with an image representation (which is
essentially the output of the object detector) pays more attention to
nouns. This is not at all surprising, it just reflects the different
training objectives. The fact that the hidden units respond to
specific n-grams is also expected; most people already believe that
RNNs are good at approximating n-gram models; the question is, can
they model more elaborate syntactic structures?
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  \todo[inline]{address}
\end{quote}
\begin{verbatim}

This is really the question that the authors should explore, e.g., by
testing whether the model can learn long distance dependencies,
agreement, recursion, word order. An example for recent work that goes
in this direction is Linzen et al. (2016).
\end{verbatim}  
\begin{quote}
\textsc{Author Response:} We have expanded the related work 
(Section~\ref{sec:related}) with a discussion of Linzen et al. (2016) 
and a few other relevant articles that came out while our submission was under review.
\end{quote}
\begin{verbatim}

Another limitation of the paper is its focus on one particular model,
which happens to be the authors'. To be convincing, the paper would
really need to compare results for this model with results for other
architectures, showing that the proposed analysis methods offer real
discriminative power.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  Due to space and time limitations we have to 
leave the comparison with other architectures for future work; however we 
have expanded the discussion of the generalizability of our techniques to other
architectures in Discussion (Section~\ref{sec:conclusion}).
\end{quote}
\begin{verbatim}

Related to this, it is not clear to me why a multimodal, multitask
model such as Imaginet is required for the work presented
here. Surely, similar results would be obtained if two unimodal RNN
models were trained, one on image descriptions to predict the next
word, and one on image representations to predict the description.
\end{verbatim}  
\begin{quote}
\textsc{Author Response:}  The motivation for using {\sc Imaginet} is laid
out in the introduction. The main point is that this model consists of
two loosely coupled pathways: One ({\sc Textual}) is a language
model which is a type of network widely used and reasonably well
understood. The other one ({\sc Visual}) is a visually-grounded encoder,
a much less commonly used and studied type of network. By using {\sc
  Imaginet} we can apply our methods to these two network types and
compare the results head-to-head. Thus {\sc Textual} serves
mostly to show that our methods give reasonably, expected answers,
while with {\sc Visual} we can generate novel, previously unfamiliar
insights. The multitask setup is not strictly
necessary for this; in order to abstract away from the effect of multitask
training on {\sc Textual} we have now added experiments on a
standalone language model {\sc LM}.

%\todo[inline]{address}
\end{quote}
\begin{verbatim}

### 2017-05-31 doc/intro.tex

\begin{abstract}

\todo[inline]{revise abstract}
  We present novel methods for analyzing the activation patterns of
  RNNs from a linguistic point of view and explore the types of 
  linguistic structure they learn. As a case study, we use a multi-task gated
  recurrent network architecture consisting of two parallel pathways with
  shared word embeddings trained on predicting the
  representations of the visual scene corresponding to an input
  sentence, and predicting the next word in the same sentence. 
  We propose a method for estimating the amount of contribution
  of individual tokens in the input to the final prediction of the networks.   
  We show that the image prediction pathway: a) is sensitive to
  the information structure of the sentence, b) pays
  selective attention to lexical categories and grammatical functions
  that carry semantic information, and c) learns to treat the same
  input token differently depending on its grammatical functions in
  the sentence. In contrast the language model is comparatively more
  sensitive to words with a syntactic function. 
  Furthermore, we propose methods to explore the function
  of individual hidden units in RNNs and show that the two pathways
  of the architecture in our case study contain
  specialized units tuned to patterns informative
  for the task, some of which can carry activations to later time
  steps to encode long-term dependencies.

@@

The present paper develops novel methods for uncovering abstract
linguistic knowledge encoded by the distributed representations of RNNs,
with a specific focus on analyzing the hidden activation patterns rather 
than word embeddings and on the syntactic generalizations 
that models learn to capture. In the current work we apply our methods
to a specific architecture trained on specific tasks, but also provide
pointers about how to generalize the proposed analysis to other settings.\label{generalintro}

@@

Our experiments show that the image prediction pathway in general 
pays special attention to syntactic categories which carry semantic 
content, and particularly nouns. More surprisingly, this pathway also 
learns to treat word types differently depending on their 
grammatical function and their position in the sequential structure of 
the sentence. In contrast, the textual pathway and the standalone 
language model are especially sensitive to the local syntactic 
characteristics of the input sentences.
\todo[inline]{say something about the findings of the last experiment.}

>>>>

\begin{abstract}
  We present novel methods for analyzing the activation patterns of
  RNNs from a linguistic point of view and explore the types of 
  linguistic structure they learn. As a case study, we use a multi-task gated
  recurrent network architecture consisting of two parallel pathways with
  shared word embeddings trained on predicting the
  representations of the visual scene corresponding to an input
  sentence, and predicting the next word in the same sentence, 
  in addition to a standard standalone language model. 
  We propose a method for estimating the amount of contribution
  of individual tokens in the input to the final prediction of the networks.   
  Using this method, we show that the image prediction pathway pays
  selective attention to lexical categories and grammatical functions
  that carry semantic information, and also learns to treat word types 
  differently depending on their grammatical function and their position 
  in the sequential structure of the sentence. In contrast, the language 
  models are comparatively more sensitive to words with a syntactic 
  function. Further analysis of the most informative n-gram contexts for 
  each model shows that in comparison to the image prediction pathway,
  the language models react more strongly to abstract contexts 
  that represent syntactic constructions. 
%  Furthermore, we propose methods to explore the function
%  of individual hidden units in RNNs and show that the two pathways
%  of the architecture in our case study contain
%  specialized units tuned to patterns informative
%  for the task, some of which can carry activations to later time
%  steps to encode long-term dependencies.

@@

The present paper develops novel methods for uncovering abstract
linguistic knowledge encoded by the distributed representations of RNNs,
with a specific focus on analyzing the hidden activation patterns rather 
than word embeddings and on the syntactic generalizations 
that models learn to capture. In the current work we apply our methods
to a specific architecture trained on specific tasks, but also provide
pointers about how to generalize the proposed analysis to other settings.

@@

Our experiments show that the image prediction pathway in general 
pays special attention to syntactic categories which carry semantic 
content, and particularly nouns. More surprisingly, this pathway also 
learns to treat word types differently depending on their 
grammatical function and their position in the sequential structure of 
the sentence. In contrast, the textual pathway and the standalone 
language model are especially sensitive to the local syntactic 
characteristics of the input sentences.  Further analysis of the most 
informative n-gram contexts for each model shows that while the image 
prediction pathway is mostly sensitive to lexical (i.e., token n-gram) 
contexts, the language models react more strongly to abstract contexts
(i.e., dependency relation n-grams) that represent syntactic constructions.
